Yelp Academic Dataset Final Report

### 2016-08-09 paper/paper.Rmd
jitter

```{r business, echo = FALSE, fig.align = "center", message = FALSE, fig.height = 3.5, warning = FALSE}
ggplot(ratings_business,aes(x=stars, y=count)) +  
  geom_point(col = rgb(0,0,1,0.25), pch = 16, cex = 2) +
  scale_y_continuous(limits=c(300,5000)) +
  xlab("Star Ratings") + 
  ylab("Review Counts") +
  theme(text = element_text(family = "Times New Roman"))

>>>>

```{r business, echo = F, fig.align = "center", message = F, fig.height = 3.5, warning = F}
ggplot(ratings_business, aes(x = stars, y = count)) +  
  geom_jitter(col = rgb(0, 0, 1, 0.25), pch = 16, cex = 2, width = 0.25) +
  scale_y_continuous(limits = c(300, 5000)) +
  xlab("Star Ratings") + 
  ylab("Review Counts") +
  theme(text = element_text(family = "Times New Roman"))
